---
title: "Exam"
author: "Rida Fathima"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Honor Code
I have neither given nor received aid on this examination, nor have I concealed any violation of the Honor Code.\


1)

#a)
```{r}
xbar = 68.55
s2 = 12.64
n= 20
alpha = 0.1
talpha0.5 = qt(alpha/2,n-1, lower.tail=F)
lb = xbar - talpha0.5*sqrt(s2/n)
ub = xbar + talpha0.5*sqrt(s2/n)

print(paste("[lb:," ,round(lb,4),',ub:',round(ub,4),']'))

```
#answer is lb = 67.1754, ub =69.9246

1.b)
```{r}
alpha= 0.1
n = 20
xbar = 68.55
zalpha0.5 = qnorm(alpha/2,lower.tail=F)
std = 3.27
lb1 = xbar - zalpha0.5*(std/sqrt(n))
ub1 = xbar + zalpha0.5*(std/sqrt(n))

print(paste("[lb:," ,round(lb1,4),',ub:',round(ub1,4),']'))

```
#answer is lb = 67.3473, ub =69.7527\
1.c)\
ub3 - lb3 =1  (Given that interval should be of 1 inch)\
ub3 = xbar + zalpha0.5*(std/sqrt(n))\
1+lb3 = xbar + zalpha0.5*(std/sqrt(n)) #-----1.\
lb3 = xbar - zalpha0.5*(std/sqrt(n)) #----------2.\
subtracting 2 and 1\
1 = 2 * zalpha0.5 * (std/sqrt(n))\
```{r}


n = (2*zalpha0.5*std)^2
n



```
#answer is n = 116\
1.d)

```{r}

df = data.frame()
a = seq(120,160,1)
for (i in a){

  talpha0.5 = qt(alpha/2,i-1, lower.tail=F)
  lb =  xbar - talpha0.5*sqrt(s2/i)
  ub =  xbar + talpha0.5*sqrt(s2/i)
  df1 = data.frame(n=i, lb =lb,ub=ub,difference = abs(ub-lb)
                   ,close_diff = abs(ub-lb)-1)
  
  
  df = rbind(df,df1)
  

}

plot(a,df$close_diff)
df$n[abs(df$close_diff)==min(abs(df$close_diff))]


```
Explanation:
Hence at n=139, we get the confidence interval difference closest to 1 inch.

This number is Not sufficient as the interval difference comes to 0.9987314\  

However, if we increase or decrease the n value, the interval difference goes further away from 1 inch.




----

2)\

```{r}
n= 12
x = c(6.0, 6.4, 7.0, 5.8, 6.0, 5.8, 5.9, 6.7, 7.1, 6.5, 6.3, 5.8)
alpha = 0.01
sig = var(x)
```
2.a)
```{r}
chisq0.5.1 = qchisq(alpha/2,n-1,lower.tail=F)
chisq0.5.2 = qchisq(alpha/2,n-1,lower.tail=T)

lb = ((n-1)*sig)/chisq0.5.1
ub = ((n-1)*sig)/chisq0.5.2

print(paste("[lb:," ,round(lb,4),',ub:',round(ub,4),']'))
```
#Answer is : lb = 0.0905 and ub = 0.9306

Hence, we are 99% confident that the variance of the plasma cholesterol levels is between [0.0905,0.9306]

2.b)

Assumptions:\
It is assumed that the data is normally distributed. This can be checked using Shapiro-Wilk test.
```{r}
shapiro.test(x)
```
Here P-value is greater than alpha. Hence the data is normally distributed
```{r}
qqnorm(x)
qqline(x)
```

Using the above plots, we can say that the data is somewhat normally distributed.\
We have also assumed, to construct a two sided confidence interval.\

3.a)
```{r}

library(readxl)
x = read_excel("C:/Users/Rida/Documents/Final_Exam.xlsx", 1)$R
shapiro.test(x)

#here x is the coefficient of restitution data
```
here P-value is greater than alpha = 0.01. Hence it is said to be normally distributed.

```{r}
qqnorm(x)
qqline(x)
```
From the above plots we can say that the data is normally distributed.\

Hence, there is enough evidence to support the assumption that the coefficient of restitution is normally distributed.

3.b)\
h0: mu =0
ha: mu >0.62
```{r}
alpha = 0.01
n= length(x)
talpha = qt(alpha, n-1,lower.tail=F)
talpha
xbar = mean(x)
s = sd(x)
t0 = (xbar - 0.62)/(s/sqrt(n))
t0

```

#t0 = 2.687 and talpha = 2.42

Here, t0 is greater than talpha. So we reject the Null Hypothesis.\
Hence, we claim that R(coefficient of restitution) exceeds 0.62.\

3.c)\
```{r}
p.value = pt(t0,n-1,lower.tail=F)
p.value
```
#P.value = 0.0052

Since, P-value is less than alpha, We reject Null Hypothesis.\
Hence, we claim that R(coefficient of restitution) exceeds 0.62.

3.d)\
Given = true mean coefficient of restitution is as high as
0.63
```{r}
library("pwr")
pwr.t.test(n=n, d=(0.63-0.62)/s, alternative = "greater", type='one.sample', sig.level=0.01)
```
#We get power =0.994 

Another approach:\
 
```{r}
delta = ((0.01)*sqrt(n))/s
a= talpha -delta

beta = pt(a,n-1)

power  = 1-beta
power


```
#Power = 0.9936 which is almost around 0.994

3.e)\
Given: power = 0.75,
true mean coefficient of restitution = 0.63

```{r}

pwr.t.test(power=0.75,d=(0.63-0.62)/s , alternative = "greater", type='one.sample', sig.level=0.01)
```

#From here we get n =17\
#hence n = 17 is required to detect a true mean coefficient of restitution as high as 0.63, if we want the power of the test to be at least 0.75

4)\
```{r}
data = data.frame(
  Flow = c(125,125,125,125,125,125,160,160,160,160,160,160,250,250,250,250,250,250),
  Observation = c(2.7,3.6,2.6,3,3.2,3.8,4.9,4.6,5,4.8,3.6,4.2,4.6,3.4,2.9,3.8,4.1,5.1)
)
  
data$Flow = factor(data$Flow)
str(data)
```

4.a)\

For Bartlett test:\

H0:	σ1^2 = σ2^2 = ... = σk^2\
Ha:	σi^2 ≠ σj^2    for at least one pair (i,j).
```{r}
boxplot(Observation~Flow, data = data)
bartlett.test(Observation~ Flow,data=data)

```
#Here it is assumed that the data is coming form a normal distribution and the observations are independent of each other.\

p-value is greater than alpha. \
So, we fail to reject the Null Hypothesis which states that all Variances are same.\
Therefore, the variances are same\

for Hypothesis test in ANOVA:\

H0: μ1 = μ2 = μ3 ... = μk\
H1: Means are not all equal.\


```{r}

data.ANOVA = aov(Observation~Flow,data=data)
summary(data.ANOVA)


```

Here, the P-value is less than alpha.\
therefore, we reject Null Hypothesis of ANOVA test\
hence, the mean values of different C2F6 flow rates are different.\

Hence, Changing the C2f6 flow rate will have an affect on the etch uniformity.



4.b)\

It is assumed that the residuals are normally and independently distributed with the same variance for
each treatment or C2F6 Flow rate.\

```{r}

a = data.ANOVA$residuals
plot(a)
```
from the above plot we infer that the residuals have no specific pattern to follow.
Hence, we can say that they are homogeneous.
```{r}
qqnorm(a)
qqline(a)
```

From the above plots we say that the residuals are normally distributed.\



```{r}
shapiro.test(a)

```

From shapiro wilk test, we see that P value is grater than alpha =0.05.\
Hence, we conclude that Residuals are normally distributed.\

Hence, no, The residuals do not indicate any problem with the underlying assumptions.\


4.c)\


H0 : µi = µj\
H1 : µi != µj\
```{r}
alpha = 0.05
n = 6
MSE = 0.3834
talpha0.5 = qt(0.05/2,18-3,lower.tail=F)
LSD = talpha0.5*sqrt(2*MSE/n)
LSD
```
#LSD = 0.7619
```{r}

y1 = c(2.7,3.6,2.6,3,3.2,3.8)
y2 = c(4.9,4.6,5,4.8,3.6,4.2)
y3 = c(4.6,3.4,2.9,3.8,4.1,5.1)
y1bar = mean(y1)
y2bar = mean(y2)
y3bar = mean(y3)

a = abs(y1bar-y2bar)
a

b = abs(y2bar-y3bar)
b

c = abs(y3bar-y1bar)
c
```

Here we see that 'a' and 'c' are greater than LSD. Hence, we reject Null Hypothesis.\
Hence for 125 - 160 and 125-250 Mean values are different.\

Here 'b' is less than LSD. So, we fail to reject its Null Hypothesis.\
160-250 Mean values are same.\


4.d)
```{r}
sig2 = 0.5
groupmeans=c(3.3,4.4,4.0)
power.anova.test(groups=length(groupmeans),between.var = var(groupmeans),within.var = sig2, sig.level = 0.05,n=6)

```


The probability of detecting the effect of C2F6 flow rate on etch uniformity in this experiment is 0.589 (around 58.9%)

